---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# probably

[![Travis build status](https://travis-ci.org/topepo/probably.svg?branch=master)](https://travis-ci.org/topepo/probably)
[![Codecov test coverage](https://codecov.io/gh/topepo/probably/branch/master/graph/badge.svg)](https://codecov.io/gh/topepo/probably?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Introduction

`probably` contains tools to facilitate activities such as:

 * exploration and visualization of class probability distributions,
 * conversion of probabilities to discrete class predictions,
 * investigate and estimate optimal probability thresholds,
 * inclusion of _equivocal zones_ where the probabilities are too uncertain to report a prediction, 
 * recalibration of class probabilities.  

## Installation

You can install `probably` from GitHub with:

```{r, eval = FALSE}
devtools::install_github("topepo/probably")
```
