---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# probably

[![Travis build status](https://travis-ci.org/topepo/probably.svg?branch=master)](https://travis-ci.org/topepo/probably)
[![Codecov test coverage](https://codecov.io/gh/topepo/probably/branch/master/graph/badge.svg)](https://codecov.io/gh/topepo/probably?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Introduction

probably contains tools to facilitate activities such as:

* Conversion of probabilities to discrete class predictions.

* Investigate and estimate optimal probability thresholds.

* Inclusion of _equivocal zones_ where the probabilities are too uncertain to report a prediction.

## Installation

You can install probably from GitHub with:

```{r, eval = FALSE}
devtools::install_github("topepo/probably")
```

## Examples

Good places to look for examples of probably are the vignettes.

* `vignette("equivocal-zones", "probably")` discusses the new `class_pred` class that probably provides for working with equivocal zones.

* `vignette("where-to-use", "probably")` discusses how probably fits in with the rest of the tidymodels ecosystem, and provides an example of optimizing class probability thresholds.
